---
title: "Costs"
author: "Jeffrey Goldberg"
date: "4/29/2019"
output: html_document
---

## Prelimaries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

R is a messy language. Let's find a more functional way to use it with [tidyverse](https://www.tidyverse.org). And some other libraries we'll use.

```{r libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
```
## Basic costs

We have [previously calculated](https://discussions.agilebits.com/discussion/comment/470503/#Comment_470503) the cost to check \(2^{32}\) guesses is six US dollars. At some point in the future that cost calculation should be put into this document. For now we will take that as a given constant.

```{r USDper32bits}
usdPer32bit <- 6.00
```

We will also use a simple function for getting from bits to cost to crack. If it turns out that the the name is only used in a few places, we can ditch its name and use it anonymously. The -1 in there is to reflect that on average the attacker only needs to go through half of the search space.

```{r bits2cost}
bits2cost <- function(b) {
  usdPer32bit * 2^((b - 32) - 1)
}
```

## Password data

Now we should also create some data of different kinds of passwords generated in different ways. The `bits` column is calculated using the the not even ready for beta [command-line wrapper](https://github.com/1Password/spg/tree/master/cmd/opgen) for the [1Password Strong Password Generator](https://github.com/1Password/spg "Github: 1Password SPG").

The field names from the datafile [pwds.csv](./pwds.csv):

- `type`: Is this a character based password (`"char"`) or a wordlist based one (`"word"`)
- `length`: Number of characters or words
- `w.sep`: Word separator (applicaple to wordlist passwords only)
- `c.ucase`: Uppercase letters allowed (applicaple to character passwords only)
- `c.lcase`: Uppercase letters allowed (applicaple to character passwords only)
- `c.digit`: Digits allowed (applicaple to character passwords only)
- `bits`: Strength of generated password in bits. (Computed by SPG)
- `sample`: An example generated password
- `exposed`: Is available to the 1Password user in the client apps

```{r readr-coltypes}
ct <- cols(
  type = col_factor(),
  length = col_integer(),
  w.sep = col_factor(),
  c.ucase = col_logical(),
  c.lcase = col_logical(),
  c.digit = col_logical(),
  bits = col_double(),
  sample = col_character(),
  exposed = col_logical()
)
```

Read in the data. Note that `read.csv()` and `read_csv()` are different functions from different libraries. We want `read_csv()` from the `readr` package.
```{r read_csv}
pwd <- read_csv("pwds.csv", col_types=ct)
```

And we will take a look at what we have loaded

```{r}
pwd
```

## Wordy description of the generation scheme

It would be nice to translate things like `type:"char", units:8, allow.lcase:TRUE, ...` into something like "8 character password with lowercase, digits" for friendlier display. So we create this ugly scaler function which will have to be wrapped in an `mapply()` later.

```{r method-words}
method_words <- function(type="word", length=4, separator="-", ucase=TRUE, lcase=TRUE, digit=TRUE) {
  # I should learn how to do idiomatic switch/case in R, but oh well.
  if(type == "word") {
    part1 = paste(length, "words")
    if (separator == "digit") {
      part2 = "digit separator"
    } else if (separator == "") {
      part2 = "no separator"
    } else {
      part2 = "constant separator"
    }
    return (paste(part1, part2, sep=", "))
  } else if(type == "char") {
    part1 = paste(length, "characters")
    d <- c("uppercase", "lowercase", "digits")
    alloweds = paste(d[c(ucase,lcase,digit)], collapse=", ")
    part2 = paste("with ", alloweds)
    return (paste(part1, part2, sep = ", "))
  }
  else {
    return("type must be \"char\" or \"word\"")
  }
}
 
```

## Computation and prepping for display

Let's create a simple function to get prettier printing of the cost. 
```{r pretty-cost}
prettyCost <- function(cost) {
  prettyNum(signif(cost, digits=2), big.mark = ",", scientific=FALSE)
}
```

And now what we have all of the pieces, we can perform the data transformations and computation and generate a tolerable looking table.

### Data transformation

This is a long pipeline, but the components of the pipe are

1. Only include cases whose strength (in bits) is between 42 and 72.
2. Calculate costs
3. Get costs more human readable numbers
4. Create textual description of generation method
4. Select which columns we want in the output
5. Sort (ascending) by strength

```{r cost-comp}
costs_small <- pwd %>% 
  filter(between(bits, 42, 72)) %>%
  mutate(cost = bits2cost(bits)) %>%
  mutate(pretty = prettyCost(cost)) %>%
  mutate(method = mapply(method_words, type, length, w.sep, c.ucase, c.lcase, c.digit)) %>%
  select(method,  bits, pretty, sample) %>%
  arrange(bits)
```

### Prettification and display

And now we construct the final table
```{r cost-table}
final_table <- kable(costs_small,
      col.names = c("Method", "Bits", "Cost (USD)", "Example"),
      align = "lrrl",
      caption ="Cracking cost for different generation schemes") %>%
  column_spec(column=4, monospace = T) %>%
  kable_styling(bootstrap_options = c("striped"), fixed_thead = TRUE)
```

```{r print-table}
final_table
```

And let's save a copy of the table as a stand-alone HTML document.
```{r save-table}
save_kable(final_table, "cost_table.html", self_contained = TRUE)
```