---
title: "Costs"
author: "Jeffrey Goldberg"
date: "4/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, warning=FALSE, message=FALSE}
library(tidyverse)
```
## R Markdown

We have [previously calculated](https://discussions.agilebits.com/discussion/comment/470503/#Comment_470503) the cost to check \(2^{32}\) guesses is six US dollars. At some point in the future that cost calculation should be put into this document. For now we will take that as a given constant.

```{r USDper32bits}
usdPer32bit <- 6.00
```

We will also use a simple function for getting from bits to cost to crack.

```{r bits2cost}
bits2cost <- function(b) {
  usdPer32bit * 2^(b - 32)
}
```

Now we should also create some data of different kinds of passwords generated in different ways.

```{r wordlist}
pwdKinds <- data.frame(
  kind = c("3 word", "4 word", "5 word"),
  bits = c(42.48, 56.65, 70.81),
  sample = c("prithee-insured-buoyant", "align-caught-boycott-delete", "boo-canter-hayseed-grudging-screech"),
  stringsAsFactors=FALSE)
```

Now lets compute the costs for the passwords kinds that we've created.

```{r cost-comp}
pwdKinds %>% 
  mutate(cost = bits2cost(bits))
```
